Pulling oral and IV data from CvTdb

### 2024-05-15 data-raw/RestrictiveClearance_comparison.Rmd
Changes to cvt object to include Showa, and new selection of fitting options has been done.

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)

@@

# Multidplyr error because of forgotten browser() call within log_likelihood
new_pk$fit %>% unnest(fit) %>% View()

saveRDS(new_pk, "data-raw/someCVT_wHTTK_JOINT.rds")

@@

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           # model = "model_2comp_nonrest",
           n_interp = 10)

@@

# Original data, filtered for common_chems
# par_DF
my_kelim_prefit <- my_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim",
         Chemical %in% common_chems) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

my_kelim_fit <- coef(my_pk) %>%
  inner_join(get_winning_model(my_pk)) %>%
  ungroup() %>%
  distinct(model, Chemical, Species, kelim) %>%
  rename(fit_kelim = "kelim") %>%
  filter(Chemical %in% common_chems)

@@

httk_df <- rest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_restrictive = "start") %>%
  inner_join(
    nonrest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_nonrestrictive = "start"))

@@

```{r}
my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE)

my_tkstats %>% filter(Species %in% "rat",
                      Route %in% "oral") %>%
  distinct(Chemical, Species, Route, Media, model, Fgutabs.tkstats) %>%
  filter(Fgutabs.tkstats > 0) %>%
  left_join(distinct(cas_convert)) %>% 
  arrange(Chemical) %>% clipr::write_clip()

pesticides <- read_csv("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Chemical List EPAPCS-2024-04-17.csv") %>%
  pull(DTXSID) %>% str_extract("DTXSID\\d+")

unique(my_tkstats$Chemical)[unique(my_tkstats$Chemical) %in% pesticides]

@@

```{r reformMod}
new_pk$fit %>% unnest(fit) %>%
  mutate(Clint = ifelse(model == "model_1comp", kelim/Vdist, Clint)) %>%
  select(Chemical, Species, model, Clint) %>%
  pivot_wider(names_from = model, values_from = Clint) %>%
  left_join(new_pk$prefit$par_DF %>%
              filter(param_name == "Clint") %>%
              select(Chemical, Species, model, start) %>%
              mutate(model = paste0("start_", model)) %>%
              pivot_wider(names_from = model,
                          values_from = start)) %>% View()

get_tkstats(new_pk)

>>>>

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)

@@

# Multidplyr error because of forgotten browser() call within log_likelihood
new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()

saveRDS(new_pk, "data-raw/someCVT_wHTTK_reform_JOINT.rds")

@@

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           n_interp = 10)

@@

# Original data, filtered for common_chems
# par_DF
my_kelim_prefit <- my_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim",
         Chemical %in% common_chems_dawson) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

my_kelim_fit <- coef(my_pk) %>%
  inner_join(get_winning_model(my_pk)) %>%
  ungroup() %>%
  distinct(model, Chemical, Species, kelim) %>%
  rename(fit_kelim = "kelim") %>%
  filter(Chemical %in% common_chems_dawson)

@@

httk_df <- new_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_restrictive = "start") %>%
  inner_join(
    nonrest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_nonrestrictive = "start"))

@@

@@

```{r reformMod}
get_tkstats(new_pk) %>% 
  distinct(Chemical, Species, model, CLtot) %>%
  pivot_wider(names_from = model, values_from = CLtot) %>%
  left_join(new_pk$prefit$par_DF %>%
              filter(param_name == "CLtot") %>%
              select(Chemical, Species, model, start) %>%
              mutate(model = paste0("start_", model)) %>%
              pivot_wider(names_from = model,
                          values_from = start)) %>% View("Clearance")

new_cl_tkstats <- get_tkstats(new_pk)
my_tkstats <- my_pk %>%
  get_winning_model() %>%
  left_join(coef(my_pk)) %>%
  left_join(rsq(my_pk)) %>% distinct()
my_tkstats %>% select(-coefs_vector) %>% clipr::write_clip()
#Send the R2 too.

## Need to parameterize with gas_pbpk or new 3compartment
## To add into total clearance 
# Rb2p * Qalv/Kblood2air
```

### 2024-05-15 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Changes to cvt object to include Showa, and new selection of fitting options has been done.

```{r SQL_queries}
# Need to make this in a specified ordered
# First all IDs (so I can check them quickly)
# Note that this uses an ALIAS for each table which is later specified in
# the FROM and LEFT JOIN statments
query <- paste0(
  "SELECT distinct ",
  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",

@@

  # Filtering steps
  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
  "c.administration_route_normalized IN ('iv', 'oral')"
)

@@

names(sql_query)
# Need to change column names for this
{
  names(sql_query)[1] <- "conc_time_id"
  names(sql_query)[8] <- "series_id"
  names(sql_query)[23] <- "study_id"
  names(sql_query)[35] <- "subject_id"
  names(sql_query)[42] <- "document_id"
}

# Harmonize values for easier analysis
sql_query <- sql_query %>%
  mutate(
    species = tolower(species),
    sex = tolower(sex),
    loq = as.numeric(loq),
    n_subjects_in_series = as.numeric(n_subjects_in_series),
    dose_level_normalized = as.numeric(dose_level_normalized),
    dose_level_original = as.numeric(dose_level_original),
    dose_volume_units = stringr::str_extract(dose_volume,
                                    pattern = "(?<=[:space:]).+"),
    dose_volume = as.numeric(stringr::str_extract(dose_volume,
                                         pattern = "^(\\d|\\.)*")),
    dose_duration_units = stringr::str_extract(dose_duration,
                                      pattern = "(?<=[space]).+"),
    dose_duration = as.numeric(stringr::str_extract(dose_duration,
                                pattern = "^\\d")),
    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
  )
sql_query <- sql_query %>%
  dplyr::rename_with(~gsub(pattern = "fk_", replacement = "",
                         .x), .cols = contains("fk_"))

# Copying
cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
```

```{r counting-replicates}
count_query <- paste0(
  "SELECT DISTINCT ",
  "a.id, a.time_hr, a.conc, ",
  "b.id, b.analyte_dtxsid, ",
  "b.test_substance_dtxsid, b.conc_medium_normalized, ",
  "c.id, c.administration_route_normalized, ",
  "c.fk_extraction_document_id, c.dose_level_normalized, ",
  "d.id, d.species ",

  # Filtering steps
  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
  "c.administration_route_normalized IN ('iv', 'oral')"
)

query_db(query = count_query,
         schema = "cvt") %>%
  select(-id) %>% 
  filter(!is.na(analyte_dtxsid),
         analyte_dtxsid == test_substance_dtxsid,
         conc > 0) %>%
  distinct() %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, fk_extraction_document_id,
           dose_level_normalized) %>%
  count() %>%
  pull(n) %>% table()
```

@@

```{r data_validation}
# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
cvt_df %>% filter(other_study_identifier == "S0916") %>%
  pull(dose_level_original_units) %>% unique()
# There are still columns that are mg/kg... changing these to ug/mL
cvt_df <- cvt_df %>% mutate(
  dose_level_original_units = ifelse(
    other_study_identifier == "S0916",
    "ug/mL",
    dose_level_original_units
  )
)

# Need to convert the units to mg/kg
# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
cvt_df <- cvt_df %>%
  mutate(
    dose_level_corrected = ifelse(
      other_study_identifier %in% "S0916",
      ifelse(administration_route_normalized %in% "oral",
             dose_level_original * 5/1000,
             dose_level_original * 2/1000),
      dose_level_normalized),
    dose_level_corrected_units = "mg/kg",
    .after = dose_level_original_units)

# For this study, it was in ng/kg not mg/kg
cvt_df <- cvt_df %>%
  mutate(
    dose_level_corrected = ifelse(
      other_study_identifier %in% "S0624",
      dose_level_original * 1E-6,
      dose_level_normalized),
    .after = dose_level_original_units)

@@

# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
cvt_df <- cvt_df %>%
  mutate(loq = ifelse(
    other_study_identifier %in% "S0976",
    case_when(
      analyte_name_original %in% "Caffeine" ~ 4.00,
      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
    ),
    loq),
    loq_units = ifelse(
      other_study_identifier %in% "S0976",
      "ng/mL",
      loq_units
    ))

# Some pentachloranisole studies
# S0361 seems to have some data that has not been extracted (also for mouse)
cvt_df <- cvt_df %>%
  mutate(loq = case_when(
    # here omitted a change to a value for LOQ that doubles the minimum detected limit
    other_study_identifier %in% "S0328" ~ 1, # This is inferred from the data
    # Highest value under loq is 0.9
    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
    # The method of imputation for loq may yet need to be improved
    .default = loq
  ),
  loq_units = case_when(
    other_study_identifier %in% "S0361" ~ "ug/mL",
    other_study_identifier %in% "S0328" ~ "ug/mL",
    .default = loq_units
  ))

# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
# The initial dose was 117 nmol, 2 mCi/kg
# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
# The initial dose *I think* is in dose_level_normalized
cvt_df <- cvt_df %>%
  mutate(conc = ifelse(document_id %in% 38,
                       conc_original*dose_level_corrected,
                       conc))

@@

# Eliminate study that gave chemical each day, not single dose
# This may be used in another type of model, but right now we deal with single bolus
# Only include those that have NA or 1 for dose frequency
cvt_df <- cvt_df %>%
  filter(dose_frequency %in% c("1", NA))

# Normalize LOQ units
cvt_df <- cvt_df %>%
  mutate(loq = ifelse(
    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
# Normalize conc_sd and conc units manually
cvt_df <- cvt_df %>%
  mutate(conc_sd_normalized = case_when(
    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
    .default = conc_sd_original
  ))
# Need to normalize the ng-eq/mL sample, conc is generally already normalized
cvt_df <- cvt_df %>%
  mutate(conc = case_when(
    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
    .default = conc
  ))

cvt_df <- cvt_df %>%
  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
                                      "DTXSID10169854",
                                      "DTXSID2021103") )) # These only have 1 or 2 values

# More notes:
# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage

# This is the final filtering so that the dataset is most consistent with the
# most current near future pull in the new year
cvt_df <- cvt_df %>%
  filter(!is.na(analyte_dtxsid),
         analyte_dtxsid == test_substance_dtxsid,
         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
         !(other_study_identifier %in% c("S0916")),
         !(analyte_name_original %in% "Methemoglobin"),
         is.na(radiolabeled))

cvt_df %>%
  filter(conc > 0) %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  distinct() %>%
  count() %>% 
  ungroup() %>%
  filter(n >= 10) %>% 
  distinct(analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  arrange(analyte_dtxsid, species, document_id) %>%
  left_join(cvt_df) %>% 
  View()

cvt_df %>%
  filter(conc > 0) %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  distinct() %>%
  count() %>%
  ungroup() %>%
  count(n)
```

>>>>

```{r SQL_queries}
# Need to make this in a specified ordered
# First all IDs (so I can check them quickly)
# Note that this uses an ALIAS for each table which is later specified in
# the FROM and LEFT JOIN statments
query <- paste0(
  "SELECT distinct ",
  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
  "b.conc_medium_normalized, b.conc_medium_original, b.time_units_original, b.conc_units_original, ",
  "b.conc_units_normalized, b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted, e.curation_set_tag ",

@@

  # Filtering steps
  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') OR ",
  "b.conc_medium_original IN ('blood', 'plasma') AND ",
  "c.administration_route_normalized IN ('iv', 'oral')"
)

@@

dtxsid_query <- paste0(
  "SELECT distinct * FROM chemicals"
)

dtxsid_query <- query_db(query = dtxsid_query,
         schema = "cvt")

dq_cols <- dtxsid_query %>%
  dplyr::select("analyte_dtxsid2" = "dsstox_substance_id",
         "fk_analyzed_chemical_id" = "id",
         "analyte_name_original" = "chemical_name_original") %>%
  distinct()

glimpse(dq_cols)

names(sql_query)
# Need to change column names for this
{
  names(sql_query)[1] <- "conc_time_id"
  names(sql_query)[8] <- "series_id"
  names(sql_query)[25] <- "study_id"
  names(sql_query)[37] <- "subject_id"
  names(sql_query)[44] <- "document_id"
}

full_set <- sql_query %>%
  left_join(dq_cols, 
            by = join_by("fk_analyzed_chemical_id", "analyte_name_original")) %>%
  mutate(analyte_dtxsid = ifelse(is.na(analyte_dtxsid), analyte_dtxsid2, analyte_dtxsid)) %>%
  select(-analyte_dtxsid2)

# Harmonize values for easier analysis
cvt_df <- full_set %>%
  filter(administration_route_normalized %in% c("iv", "oral")) %>%
  mutate(
    species = tolower(species),
    sex = tolower(sex),
    loq = as.numeric(loq),
    n_subjects_in_series = as.numeric(n_subjects_in_series),
    dose_level_normalized = as.numeric(dose_level_normalized),
    dose_level_original = as.numeric(dose_level_original),
    dose_volume_units = stringr::str_extract(dose_volume,
                                    pattern = "(?<=[:space:]).+"),
    dose_volume = as.numeric(stringr::str_extract(dose_volume,
                                         pattern = "^(\\d|\\.)*")),
    dose_duration_units = stringr::str_extract(dose_duration,
                                      pattern = "(?<=[space]).+"),
    dose_duration = as.numeric(stringr::str_extract(dose_duration,
                                pattern = "^\\d")),
    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
  )

cvt_df <- cvt_df %>%
  mutate(conc_medium_normalized = ifelse(is.na(conc_medium_normalized),
                                         conc_medium_original,
                                         conc_medium_normalized))
```

@@

```{r data_validation}
# Check other_study_identifier == S0916 so that it has dose_level_units_original == ug/mL
cvt_df %>% filter(other_study_identifier == "S0916") %>%
  pull(dose_level_units_original) %>% unique()
# There are still columns that are mg/kg... changing these to ug/mL
cvt_df <- cvt_df %>% mutate(
  dose_level_units_original = ifelse(
    other_study_identifier == "S0916",
    "ug/mL",
    dose_level_units_original
  )
)
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

# Need to convert the units to mg/kg
# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
cvt_df <- cvt_df %>%
  mutate(
    dose_level_corrected = ifelse(
      other_study_identifier %in% "S0916",
      ifelse(administration_route_normalized %in% "oral",
             dose_level_original * 5/1000,
             dose_level_original * 2/1000),
      dose_level_normalized),
    dose_level_corrected_units = "mg/kg",
    .after = dose_level_units_original)

# For this study, it was in ng/kg not mg/kg
cvt_df <- cvt_df %>%
  mutate(
    dose_level_corrected = ifelse(
      other_study_identifier %in% "S0624",
      dose_level_original * 1E-6,
      dose_level_normalized),
    .after = dose_level_units_original)

cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

@@

# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
cvt_df <- cvt_df %>%
  mutate(loq = ifelse(
    other_study_identifier %in% "S0976",
    case_when(
      analyte_name_original %in% "Caffeine" ~ 4.00,
      analyte_name_original %in% "L-Ephedrine" ~ 3.39,
      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
    ),
    loq),
    loq_units = ifelse(
      other_study_identifier %in% "S0976",
      "ng/mL",
      loq_units
    ),
    conc_units_original = ifelse(other_study_identifier %in% "S0976", "mg/L", conc_units_original))

# Some pentachloranisole studies
# S0361 seems to have some data that has not been extracted (also for mouse)
cvt_df <- cvt_df %>%
  mutate(loq = case_when(
    # here omitted a change to a value for LOQ that doubles the minimum detected limit
    other_study_identifier %in% "S0328" ~ 1, # This is inferred from the data
    # Highest value under loq is 0.9
    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
    # The method of imputation for loq may yet need to be improved
    .default = loq
  ),
  loq_units = case_when(
    other_study_identifier %in% "S0361" ~ "ug/mL",
    other_study_identifier %in% "S0328" ~ "ug/mL",
    .default = loq_units
  ))
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
# The initial dose was 117 nmol, 2 mCi/kg
# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
# The initial dose *I think* is in dose_level_normalized
cvt_df <- cvt_df %>%
  mutate(conc = as.numeric(conc),
         conc_original = as.numeric(conc)) %>%
  mutate(conc = ifelse(document_id %in% 38,
                       conc_original*dose_level_corrected,
                       conc))

@@

# Eliminate study that gave chemical each day, not single dose
# This may be used in another type of model, but right now we deal with single bolus
# Only include those that have NA or 1 for dose frequency
cvt_df <- cvt_df %>%
  filter(dose_frequency %in% c("1", NA))
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

cvt_df$loq_units %>% unique()
# Normalize LOQ units
cvt_df <- cvt_df %>%
  mutate(loq = ifelse(
    loq_units %in% c("ug/L", "ng/mL", "ng/g"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
# Normalize conc_sd and conc units manually
cvt_df <- cvt_df %>%
  mutate(conc_sd_original = as.numeric(conc_sd_original)) %>%
  mutate(conc_sd_normalized = case_when(
    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml", "ng/g", "ng/g tissue", "ug/L") ~ conc_sd_original*1E-3,
    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
    .default = conc_sd_original
  ))
# Need to normalize the ng-eq/mL sample, conc is generally already normalized
cvt_df <- cvt_df %>%
  mutate(conc = case_when(
    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
                               "ng/g", "ng/g tissue", "ug/L") ~ conc_original*1E-3,
    conc_units_original %in% c("g/dL") ~ conc_original*1E-4,
    conc_units_original %in% c("pg/mL") ~ conc_original*1E-6,
    .default = conc
  ))
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
# Some chemicals have very few values
cvt_df <- cvt_df %>%
  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
                                      "DTXSID10169854",
                                      "DTXSID2021103",
                                      "DTXSID6038299") ),
                administration_route_normalized %in% c("iv", "oral"))
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
# More notes:
# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
cvt_df %>% count(curation_set_tag)

# This is the final filtering so that the dataset is most consistent with the
# most current near future pull in the new year
cvt_df <- cvt_df %>%
  filter(!is.na(analyte_dtxsid),
         fk_analyzed_chemical_id == fk_dosed_chemical_id, # sometimes test chemical id is not filled out :/
         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
         !(other_study_identifier %in% c("S0916")),
         !(analyte_name_original %in% "methemoglobin"),
         radiolabeled %in% c(NA, FALSE) # Legacy left as NA, other curations explicitly state FALSE
         )
cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

cvt_df %>%
  pull(conc_units_original) %>%
  table()
cvt_df %>%
  filter(conc_units_original %in% "molar percentage") %>% View()

cvt_df <- cvt_df %>%
  filter(!is.na(conc)) %>%
  mutate(conc = case_when(
    conc_units_original %in% "umol/kg" ~ conc * dose_level_corrected,
    # Some concentration values are in uM
    document_id %in% 62 ~ conc * 179.219/1E3,
    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc * 88.15/1E3,
    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc * 102.177/1E3,
    .default = conc
  )) %>%
    mutate(conc_sd_normalized = case_when(
    conc_units_original %in% "umol/kg" ~ conc_sd_original * dose_level_corrected,
    # Some concentration values are in uM
    document_id %in% 62 ~ conc_sd_original * 179.219/1E3,
    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc_sd_original * 88.15/1E3,
    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc_sd_original * 102.177/1E3,
    .default = conc_sd_original
  ))
cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
```
